---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AustraliaCOVID19

<!-- badges: start -->
[![R build status](https://github.com/etc5523-2020/r-package-assessment-yliu0320/workflows/R-CMD-check/badge.svg)](https://github.com/etc5523-2020/r-package-assessment-yliu0320/actions)
<!-- badges: end -->

The goal of AustraliaCOVID19 is to see the coronavirus data of daily cases and cumulative cases of different types in different states of Australia between 2020-01-12 to 2020-10-02.Besides,the shiny app in this package will give people the whole information about the data with the interactive plots and table.

## Installation

You can install the AustraliaCOVID19 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2020/r-package-assessment-yliu0320")
```
## Example

This is a basic example which shows the content of data in the package. 

```{r example}
library(AustraliaCOVID19)
library(tibble)
coronavirus_region
n_states(coronavirus_region)
```

